\section{Comparison of {\sys} and Tamaraw}
\label{appendix:tamaraw}
%Prior work has proposed several shaping strategies, although many of them use ad
%hoc heuristics for shaping various features of network traffic to mitigate
%network side-channel leaks.
%Among prior work on shaping strategies to mitigate network side channels,
{\small
Tamaraw \cite{cai2014tamaraw} provides a
mathematical notion of privacy guarantee of a shaping strategy, called
$\epsilon$-security.
To disambiguate with {\sys}'s notion of
$(\varepsilon, \delta)$-DP, we rename Tamaraw's $\epsilon$
variable with $\gamma$.
We show that {\sys}'s $(\varepsilon, \delta)$-DP definition
is strictly stronger than Tamaraw's $\gamma$-security definition.

First, we explain Tamaraw's $\gamma$-security definition.
In Tamaraw, $W$ is a random variable representing the label of a
traffic trace.
For a trace $w$, the random variables $T_{w}$ and $T_{w}^{D}$ respectively
represent the packet trace of $w$ before and after shaping with a defense $D$.
The distribution of $T_{w}^D$ captures all variations in the observed
shape of $w$ resulting from both the defense mechanism and the
network, while the distribution of $T_{w}$ only contains variations due to
the network.
%
The attacker can measure the distribution of $W$ and $T_{w}^{D}$ independently.
%
Upon observing a network trace $t$, an optimal attack~$A$,~selects the
label of the trace with maximum likelihood of observation:
\begin{equation*}
  A(t) = \argmax_{w}{\Pr[W=w]\Pr[T_{w}^{D}=t]}
\end{equation*}
The probability that an attack $A$ outputs label $w_i$ is $\Pr_A[w_i]$.
\begin{definition*}[Tamaraw $\gamma$-privacy]
  A fingerprinting defense $D$ is said to be uniformly $\gamma$-private if for the attack $\mathcal{A}$ if we have:
  \begin{equation*}
    \max_w\big[\Pr[A(T_w^D)=w]\big] \leq \gamma
  \end{equation*}
\end{definition*}
\begin{proposition}
  Tamaraw $\gamma$-privacy is strictly weaker than the notion of
  $\varepsilon$-differential privacy.
  \label{prop:tamaraw-vs-netshaper}
\end{proposition}

To prove \Cref{prop:tamaraw-vs-netshaper}, we prove the following two lemmas.
\begin{lemma}
  There exists a Tamaraw $\gamma$-private defense mechanism that fails to
  satisfy $\varepsilon$-DP for any given value of $\varepsilon$.
\end{lemma}
\begin{proof}
%  Assume a closed-world setup of $n$ webpages.
Consider a web service with a dataset of $n$ web pages.
We propose a defense $D$, which shapes pages to a constant-rate pattern $O_c$
with probabilities $\alpha$ or $\beta$.
$D$ reshapes page $w_j$ to $O_c$ with probability $\beta$ and
all other pages $w_i \neq w_j$ with probability $\alpha$.
If a page is not shaped, it is revealed.
%\begin{enumerate}

%\end{enumerate}

The probability that any attack can correctly identify the label for $w_j$ is
upper-bounded by:  $\Pr[A(T^{D}_{w_{i=j}}) = w_j]$
\begin{align*}
  & = \Pr[A(T^D_{w_{i=j}}) = w_j |
  T^D_{w_{i=j}}=T_{w_{i=j}}]\Pr[T^D_{w_{i=j}}=T_{w_{i=j}}] +
  \\
  &~~~~\Pr[A(T^D_{w_{i=j}}) = w_j | T^D_{w_{i=j}}=O_c]\Pr[T^D_{w_{i=j}}=O_c]
  \\
  & \leq  1.(1-\beta) + \frac{1}{n}\beta = p_c^j
\end{align*}
For $(1- \frac{n\gamma - 1}{n-1}) < \beta$ we have: $p_c^j \leq \gamma$.
%
Similarly, the probability that any attack can correctly classify $w_{i\neq j}$
is upper-bounded by $p_c^i = 1-\alpha + \frac{\alpha}{n}$, and for $(1-
\frac{n\gamma - 1}{n-1}) < \alpha$ we have: $p_c^j \leq \gamma$.
Therefore, for all values of $\alpha$ and $\beta$ such that $(1- \frac{n\gamma -
1}{n-1}) < \beta < \alpha$, the probability that any attack can successfully
guess~a~page is less than $\gamma$, and
the defense is uniformly $\gamma$-private.

When the output of the algorithm is $O_{c}$, the probability of the page being
$w_j$ is $\beta$ and any other page is $\alpha$. Thus,
%\begin{equation*}
$\log(\frac{\Pr[T_{w_{i\neq j}}^{D}=O_{c}]}{\Pr[T_{w_{i=j}}^{D}=O_{c}]})
= \log(\frac{\alpha}{\beta})$.
%\end{equation*}
By setting $\alpha > {e^{\varepsilon}}\beta$, we get a mechanism that is
$\gamma$-private for Tamaraw but not $\varepsilon$-DP for {\sys}.
%Therefore, it fails to guarantee $\varepsilon$-differential privacy.
\vspace{-0.2cm}
\end{proof}
\begin{lemma}
  A $\varepsilon$-DP shaping algorithm is Tamaraw $\gamma$-private for
  $\varepsilon \leq \log(n\gamma)$.
%  \begin{equation*}
%    \varepsilon \leq \log(n\gamma)
%  \end{equation*}
\end{lemma}
\begin{proof}
For a trace $w$, the random variable $T_{w}^{DP}$ represents the packet
trace of $w$ after a differentially private shaping mechanism is applied.
%
The classification attack on shaped traffic can
%analysis the shaped traces so it can
be considered a post-processing of the results of a
differentially private shaping mechanism (i.e. defense) and, hence, is
differentially
private. Therefore, we have:
\begin{align*}
& \frac{\Pr[A(T_{w_{i}}^{DP}) = w_i]}{\Pr[A(T_{w_{j}}^{DP}) = w_i]} \leq e^
{\varepsilon}
\Rightarrow \Pr[A(T_{w_{i}}^{DP}) = w_i] \leq e^
{\varepsilon} .\Pr[A(T_{w_{j}}^{DP}) = w_i]
\end{align*}
Intuitively, this implies that the likelihood of the attacker correctly
classifying the trace with label $i$ compared to incorrectly classifying it with
label $j$ is bounded by $e^{\varepsilon}$.
The above inequality is correct for all $w_j: j\in \{1, 2, \dots, n\}$, and we
can extend the above equation to calculate the summation over $j$:
\vspace{-0.3cm}
%Extending the above equation we have:
\begin{align*}
n\times \Pr[A(T_{w_{i}}^{DP}) = w_i] \leq e^{\varepsilon}\sum_{j=1}^{n}
\Pr[A(T_{w_{j}}^{DP}) = w_i]
= e^{\varepsilon} \operatorname{Pr}_{A}[w_i].
\end{align*}
%where $\Pr_{A}[w_i]$ is the probability that attack $A$ outputs the label
%$w_i$.
Thus, for any given trace $w_i$, the probability that any attack $A$,
classifies it correctly is bounded by:
%\begin{equation*}
$\Pr[A(T_{w_{i}}^{DP}) = w_i] \leq \frac{e^{\varepsilon} \Pr_{A}[w_i]}{n}$.
%\end{equation*}
The probability that an attacker can guess the victim’s trace is bounded by:
%\begin{align*}
$\max_{w_i}{\Pr[A(T_{w_{i}}^{DP}) = w_i]} \leq \frac{e^{\varepsilon}}{n}
\max_{w_i}{\operatorname{Pr}_{A}[w_i]} \leq \frac{e^{\varepsilon}}{n} \leq
\gamma$.
%\end{align*}
\end{proof}
}
%Putting the two lemmas together, we prove that {\sys}'s DP is strictly stronger
%than Tamaraw's privacy.
